Supporting information

### 2019-09-04 EAshiklomanovSA2.Rmd
Add LL vs. climate supporting figure

>>>>

```{r ll-clim, echo = FALSE, fig.cap = ll_clim_cap, warning = FALSE}
ll_clim_cap <- paste(
  "Relationships of leaf lifespan to mean annual temperature ",
  "within a subset of PFTs,",
  "with least-squares linear regression and 95% confidence interval."
)
traits_clim <- file.path(npdir, "extdata", "traits_with_climate.rds") %>%
  readRDS() %>%
  as_tibble()
clim_dat <- traits_clim %>%
  distinct(ObservationID, Latitude, Longitude, AMT)
trait_analysis <- file.path(npdir, "extdata", "traits_analysis.rds") %>%
  readRDS() %>%
  as_tibble()
dat <- inner_join(trait_analysis, clim_dat, "ObservationID") %>%
  mutate(pft = forcats::fct_recode(clm45, !!!shiklomanov2017np::abbr2pft))
ppp <- c("BlDTe", "BlDBo", "ShDTe", "ShDBo", "NlETe", "NlEBo")

dat %>%
  filter(pft %in% ppp, !is.na(leaf_lifespan), !is.na(AMT)) %>%
  mutate(pft = factor(pft, ppp)) %>%
  ggplot() +
  aes(x = AMT, y = leaf_lifespan) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(vars(pft), scales = "free_y", dir = "v", ncol = 3) +
  labs(x = expression("Annual mean temperature" ~ (degree * C)),
       y = "Leaf lifespan (months)") +
  cowplot::theme_cowplot()

## dat %>%
##   filter(pft %in% ppp, !is.na(SLA), !is.na(AMT)) %>%
##   mutate(pft = factor(pft, ppp)) %>%
##   ggplot() +
##   aes(x = AMT, y = SLA) +
##   geom_point() +
##   geom_smooth(method = "lm") +
##   facet_wrap(vars(pft), scales = "free_y", dir = "v", ncol = 3) +
##   labs(x = expression("Annual mean temperature" ~ (degree * C)),
##        y = expression("Specific leaf area" ~ (kg ~ m^{-2}))) +
##   cowplot::theme_cowplot()

```
